---
title: "Index"
author: "Mario"
date: "07/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE)
```
# All proposed figures and Stats are at THE BOTTOM of the html



"A controlled microclimate contrast of three native and one highly invasive plant species in Southern California"


A controlled microclimate contrast of three native and one highly invasive plant species in Southern California
Mario Zuliani1*, Laura Brussa, Jessica Cunsolo, Angela Zuliani, and Christopher J. Lortie1. 
1Department of Biological Science, York University, 4700 Keele St, Toronto, ON M3J 1P3, Canada
Question: How do increasing ambient temperature in arid ecosystems influence both the successive germination and total biomass of 3 natives and 1 exotic annual plant species. 

Location: Greenhouse simulation conditions within the Carrizo Plain National Monument, California, USA (35.117985, -119.608762)

Methods: The effects of temperature were tested on 3 native, Salvia columbariae, Layia platyglossa, Phacelia tanacetifolia and 1 exotic plant species, Bromus rubens independently over a 6-week growing period in a temperature controlled greenhouse in 2021. 210 individual replicates were conducted across an increasing temperature gradient meant to simulate the arid ecosystems of Southern California. Hourly temperature was recorded through ambient temperature pendants. Annual biomass was then recorded at the conclusion of each 6-week trial.

Results: The evaluation of temperature on the overall successive germination of native and exotic annual plant species showed an overall negative affect. Increasing temperatures negatively influenced the total germination of one native – Layia platyglossa - and one exotic – Bromus rubens -  annual species. Regarding individual biomass, increases in ambient temperature negatively influenced both the overall size and biomass of 2 native – Layia platyglossa & Salvia columbaria – and one exotic – Bromus rubens - annual species.

Conclusion: These findings suggest that increases in ambient temperature due to global warming can have negative impacts on both native and exotic plant establishment and succession. Analyzing the performance and establishment of these annual species is essential to understanding local plant community composition while determining the responses both native and exotic annuals have to increasing abiotic stressors within arid/semi-arid ecosystems. Specifically understanding how increasing ambient temperature influences exotic annual establishment can be vital knowledge for managing the spread and establishment of these species.

Key Words: Intraspecific Association, Desert, Grassland, Greenhouse, Temperature, Bromus rubens, Exotic Species, Restoration

```{r}
###Packages for future work
library(rmarkdown)
library(ggmap)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(MASS)
library(ggpubr) 
library(emmeans)
```
```{r}
##Prep Temp Data
#Layia <- read.csv("All Temp Data.csv")
#Brome <- read.csv("Brome Temp Sheet.csv")
#Salvia <- read.csv("Salvia Temp Sheet.csv")
#Phacelia <- read.csv("Phacelia Temp Sheet.csv")

###Merge all species temp data
#Temp <- merge(Layia, Brome, all = TRUE)
#Temp <- merge(Temp, Salvia, all = TRUE)
#Temp <- merge(Temp, Phacelia, all = TRUE)

###Set up SD and SE
#se_temp <- sd(Temp$temperature)/sqrt(length(Temp$temperature))
#Temp$se <- se_temp

###Get mean and max temp
#Temp <- Temp %>%
  #group_by(as.character(temp), species, pendant_ID, se) %>%
  #summarise(mean_temp = mean(temperature), max_temp = max(temperature))
#names(Temp)[1] <- "temp"

###Output file
#write.csv(Temp, "Temp.csv")

```

```{r}
###Clean up Temperature and determine the mean and max for each pendant.
#Temp2 <- read.csv("Temp_2.csv")
```


```{r}
#Prep Germination Data and Combine With Temp Data
#Germ <- read.csv("Final Germination.csv")
#final <- merge(Germ, Temp2, all = TRUE)

#write.csv(final, "final.csv")
final <- read.csv("final.csv")
```


###Data Viz
```{r}
###Temperature vs Number of Germinated Individuals in 6 weeks by species
TempFactor <- ggplot(final, aes(temp, germination),show.legend=FALSE) +
  geom_boxplot() +
  facet_wrap(~species)+
  scale_color_brewer(palette = "Set1") + theme_classic() + labs(tag = "")+
  theme(axis.title.x = element_blank()) +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Number of Germinated Seeds")
TempFactor
```
```{r}
###Plotting the lm
plot(lm(germination ~ mean_temp, data = final), which = 1)
```
```{r}
germination_poly <- lm(germination ~ mean_temp + I(mean_temp^2), data = final)

library(car)
library(broom)
Anova(germination_poly)
```
```{r}
###General Figure showing Temp vs total germination in 6 weeks (Not useable)
Temp <- ggplot(final, aes(mean_temp, germination),show.legend=FALSE) +
  geom_point() +
  scale_color_brewer(palette = "Set1") + theme_classic() + 
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Number of Germinated Seeds")
Temp
```

```{r}
###Figure showing Temp vs germination by species (Not facetted)
Tempspecies <- ggplot(final, aes(mean_temp, germination, color = species),show.legend=FALSE) +
  geom_point() +
  scale_color_brewer(palette = "Set1") + theme_classic() + 
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Number of Germinated Seeds")
Tempspecies
```
```{r}
###This is Temperature vs germination, facet by species. I am not the biggest fan of this figure though
TempspeciesFacet <- ggplot(final, aes(mean_temp, germination, color = species),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~temp)+
  scale_color_brewer(palette = "Set1") + theme_classic() + 
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Number of Germinated Seeds")
TempspeciesFacet <- TempspeciesFacet + theme(legend.title = element_text(size = 3), 
               legend.text = element_text(size = 3))
TempspeciesFacet
```
ggplot(shelter.shrub.open, aes((day), temp, color=microsite)) + geom_smooth()+ xlab("Day") + ylab ("Temperature (°F)")+ theme_classic()+ theme(axis.text=element_text(size=12))+stat_summary(fun.y=max, geom="point", size=2, aes(shape = microsite))+ labs(color="Microsite", shape= "Microsite")


```{r}
###Plot for Temperature and germination in 6 weeks by species
TempspeciesFacet <- ggplot(final, aes(mean_temp, germination),show.legend=FALSE) +
  geom_smooth(method = lm) + 
  scale_color_brewer(palette = "Set1") + theme_classic() + 
    facet_wrap(~species)+
  labs(x = "Mean Temperature (°C)", y = "Mean Number of Germinations") +stat_summary(fun.y=mean, geom="point", size=1.5)
TempspeciesFacet
```
```{r}
###Figure shows temperature v Germination in 6 weeks, facet by species and filled via temperature
TempspeciesFacetColor <- ggplot(final, aes(mean_temp, germination, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species)+
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Number of Germinated Seeds")
TempspeciesFacetColor
```


```{r}
###Statistics For Germination of Each species at varying temperatures
m1 <- glm(germination ~ temp*species+mean_temp, family = "quasipoisson", data = final)
anova(m1, test = "Chisq")
###Was temp manipulated significantly in the experiment?
e1 <- emmeans(m1, pairwise~temp)
e1

###Germination by temp and species
e2 <- emmeans(m1, pairwise~temp|species) ###Low Temp brome germinates the same amount as Layia at all temps
e2
```
```{r}
###Difference in germination by species and temp
e3 <- emmeans(m1, pairwise~species|temp) ###Low Temp brome germinates the same amount as Layia at all temps
e3
```


```{r}
###Mass by Temperature 
Mass <- ggplot(final, aes(mean_temp, mass),show.legend=FALSE) +
  geom_point() +
  scale_color_brewer(palette = "Set1") + theme_classic() + 
  theme() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Mean Temperature", y = "Mass")
Mass
```
```{r}
MassSpecies <- ggplot(final, aes(mean_temp, mass, color = species),show.legend=FALSE) +
   geom_smooth(method = lm, se = TRUE) +
  scale_color_brewer(palette = "Set1") + theme_classic() + 
  stat_summary(fun.y=mean, geom="point", size=2)+
  labs(x = "Mean Temperature (°C)", y = "Mean Mass (g)")
MassSpecies
```
```{r}
MassSpeciesFacet <- ggplot(final, aes(mean_temp, mass),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species)+
  scale_color_brewer(palette = "Set1") + theme_classic() +
  theme(axis.title.x = element_blank()) +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Mass (g)")
MassSpeciesFacet
```
```{r}
###Temperature v biomass, facet by species and fill by Temp
MassSpeciesFacetColor <- ggplot(final, aes(mean_temp, mass, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species)+
  scale_color_brewer(palette = "Set1") + theme_classic() +
  theme(axis.title.x = element_blank()) +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Biomass (g)")
MassSpeciesFacetColor
```


```{r}
#Use guasian
###Biomass by temp and species
m2 <- glm(mass ~ germination*temp*species+mean_temp, family = "quasipoisson", data = final)
anova(m2, test = "Chisq")
e4 <- emmeans(m2, pairwise~temp|species)
e4

```
```{r}
###Difference in biomass by species and temp
e5 <- emmeans(m2, pairwise~species|temp)
e5

```

```{r}
#Natives Vs Invasives Germination
#Not useful
#locality <- ggplot(final, aes(mean_temp, germination, color = temp),show.legend=FALSE) +
 # geom_point() +
  #facet_wrap(~locality) +
  #scale_color_brewer(palette = "Set1") + theme_classic() +
  #geom_smooth(method = lm, se = TRUE) + 
  #labs(x = "Temperature", y = "Number of Germinated Seeds")
#locality
```
```{r}
#Not useful
#locality2 <- ggplot(final, aes(mean_temp, germination),show.legend=FALSE) +
 # geom_point() +
  #facet_wrap(~locality) +
  #scale_color_brewer(palette = "Set1") + theme_classic() +
  #geom_smooth(method = lm, se = TRUE) + 
  #labs(x = "Temperature", y = "Number of Germinated Seeds")
#locality2
```

```{r}
#Native vs Invasive Biomass
###Do not use
#locality3 <- ggplot(final, aes(mean_temp, mass, color = temp),show.legend=FALSE) +
  #geom_point() +
 # facet_wrap(~locality) +
 # scale_color_brewer(palette = "Set1") + theme_classic() +
 # geom_smooth(method = lm, se = TRUE) + 
 # labs(x = "Temperature", y = "Bimass (g)")
#locality3
```
```{r}
###Do not use
#locality4 <- ggplot(final, aes(mean_temp, mass),show.legend=FALSE) +
 # geom_point() +
  #facet_wrap(~locality) +
  #scale_color_brewer(palette = "Set1") + theme_classic() +
  #geom_smooth(method = lm, se = TRUE) + 
  #labs(x = "Temperature", y = "Biomass (g)")
#locality4
```


```{r}
#Natives vs Invasives Stats Mass
#Not useful
#m3 <- glm(mass ~ germination*temp*locality, family = "quasipoisson", data = final)
#anova(m3, test = "Chisq")
#e6 <- emmeans(m3, pairwise~locality|temp)
#e6

```
```{r}
#m4 <- glm(germination ~ temp*locality, family = "quasipoisson", data = final)
#anova(m4, test = "Chisq")
#e7 <- emmeans(m4, pairwise~locality|temp)
#e7
```

###November 24th 2022 (After meeting)
```{r}
###Boxplots Comparing Mean and Max Temp Blocks
ggplot(final, aes(x=factor (temp, level=c("Low", "Medium", "High")), mean_temp)) +
  geom_boxplot() + theme_classic() + labs(x = "Temperature Treatment", y = "Mean Temperature")

ggplot(final, aes(x=factor (temp, level=c("Low", "Medium", "High")), max_temp)) +
  geom_boxplot() + theme_classic() + labs(x = "Temperature Treatment", y = "Max Temperature")
```
```{r}
###Test Biomass by Established Density with Mean and Max Temp

###Set up Biomass by Established Density
final$average_mass <- final$mass/final$establishment

###By mean Temp
ggplot(final, aes(mean_temp, average_mass),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Bimass per Individual")

###Dont like this one
#ggplot(final, aes(mean_temp, average_mass, color = temp),show.legend=FALSE) +
 # geom_point() +
  #facet_wrap(~species) +
  #scale_color_brewer(palette = "Set1") + theme_classic() +
  #geom_smooth(method = lm, se = TRUE) + 
  #labs(x = "Temperature", y = "Bimass per Individual")

###Max Temp
ggplot(final, aes(max_temp, average_mass),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Bimass per Individual")

ggplot(final, aes(max_temp, average_mass, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Bimass per Individual")

###Ran as Gaussian since temp is blocked
m5 <- glm(average_mass ~ temp*species, family = "gaussian", data = final)
anova(m5, test = "Chisq")
e8 <- emmeans(m5, pairwise~temp|species)
e8

m6 <- glm(average_mass ~ mean_temp*species+pendant_ID, family = "quasipoisson", data = final)
anova(m6, test = "Chisq")
e9 <- emmeans(m6, pairwise~species|mean_temp)
e9

a <- glm(average_mass ~ max_temp*species+pendant_ID, family = "quasipoisson", data = final)
anova(a, test = "Chisq")
e09 <- emmeans(a, pairwise~species|max_temp)
e09
```
```{r}
###Set up percent successful establishment of individuals
final$succession <- final$establishment/final$germination
```

```{r}
### Treat Temp as Block
### Average Mass
ggplot(final, aes(mean_temp, average_mass, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Mean Temperature", y = "Bimass per Individual")

model1 <- glm(average_mass ~ temp*species, family = "quasipoisson", data = final)
anova(model1, test = "Chisq")
em1 <- emmeans(model1, pairwise~temp|species)
em1

###Succession of establishment (Established/germinated)
ggplot(final, aes(mean_temp, succession, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Mean Temperature", y = "Percent Successfully Established")

model2 <- glm(succession ~ temp*species, family = "quasipoisson", data = final)
anova(model2, test = "Chisq")
em2 <- emmeans(model2, pairwise~temp|species)
em2

###Overall Establishment
ggplot(final, aes(mean_temp, establishment, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Mean Temperature", y = "Individual Establishment")

model3 <- glm(establishment ~ temp*species, family = "quasipoisson", data = final)
anova(model3, test = "Chisq")
em3 <- emmeans(model3, pairwise~temp|species)
em3

###Overall Germination

ggplot(final, aes(mean_temp, germination, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Mean Temperature", y = "Individual Germination")

model4 <- glm(germination ~ temp*species, family = "quasipoisson", data = final)
anova(model4, test = "Chisq")
em4 <- emmeans(model4, pairwise~temp|species)
em4
```
```{r}
###Treating temp as continuous

#average mass by mean_temp
model5 <- glm(average_mass ~ mean_temp*species + pendant_ID, family = "gaussian", data = final)
anova(model5, test = "Chisq")
em5 <- emmeans(model5, pairwise~species|mean_temp)
em5

model6 <- glm(succession ~ mean_temp*species + pendant_ID, family = "gaussian", data = final)
anova(model6, test = "Chisq")
em6 <- emmeans(model6, pairwise~species|mean_temp)
em6

model7 <- glm(establishment~ mean_temp*species + pendant_ID, family = "gaussian", data = final)
anova(model7, test = "Chisq")
em7 <- emmeans(model7, pairwise~species|mean_temp)
em7

model8 <- glm(germination ~ mean_temp*species + pendant_ID, family = "gaussian", data = final)
anova(model8, test = "Chisq")
em8 <- emmeans(model8, pairwise~species|mean_temp)
em8
```
```{r}
### Test everything with Maximum Temp
# Max Temp by Average mass
ggplot(final, aes(max_temp, average_mass, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Maximum Temperature", y = "Bimass per Individual")

model9 <- glm(average_mass ~ max_temp*species, family = "quasipoisson", data = final)
anova(model9, test = "Chisq")
em9 <- emmeans(model9, pairwise~species|max_temp)
em9

###Succession of establishment (Established/germinated)
ggplot(final, aes(max_temp, succession, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Maximum Temperature", y = "Percent Successfully Established")

model10 <- glm(succession ~ max_temp*species, family = "quasipoisson", data = final)
anova(model10, test = "Chisq")
em10 <- emmeans(model10, pairwise~species|max_temp)
em10

###Overall Establishment
ggplot(final, aes(max_temp, establishment, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Maximum Temperature", y = "Number Established Individuals")

model11 <- glm(establishment ~ max_temp*species, family = "quasipoisson", data = final)
anova(model11, test = "Chisq")
em11 <- emmeans(model11, pairwise~species|max_temp)
em11

###Overall Germination

ggplot(final, aes(max_temp, germination, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Maximum Temperature", y = "Number Germinated Individuals")

model12 <- glm(germination ~ temp*species, family = "quasipoisson", data = final)
anova(model12, test = "Chisq")
em12 <- emmeans(model12, pairwise~temp|species)
em12
```
```{r}
###Test establish density by Biomass, Temp Block, and Species

#Based on number of individuals that survived germination
ggplot(final, aes(mean_temp, succession, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Temperature", y = "Successive Individuals")

model13 <- glm(succession ~ mass*temp*species, family = "quasipoisson", data = final)
anova(model13, test = "Chisq")
em13 <- emmeans(model13, pairwise~temp|species)
em13
```

```{r}
### Stats for mass
m20 <- glm(mass ~ species*temp+mean_temp+max_temp, family = "quasipoisson", data = final)
anova(m20, test = "Chisq")
e20 <- emmeans(m20, pairwise~temp|species)
e20

m21 <- glm(germination ~ temp*establishment*mass*species, family = "quasipoisson", data = final)
anova(m21, test = "Chisq")
e21 <- emmeans(m1, pairwise~temp|species)
e21

# Testing Mass, establishment, and germination with temp as a block/category by species (Need pendant ID)

m61 <- glm(mass ~ temp*species+pendant_ID, family = "quasipoisson", data = final)
anova(m61, test = "Chisq")
e91 <- emmeans(m61, pairwise~species|temp)
e91

m62 <- glm(establishment ~ temp*species+pendant_ID, family = "quasipoisson", data = final)
anova(m62, test = "Chisq")
e92 <- emmeans(m62, pairwise~species|temp)
e92

m63 <- glm(germination ~ temp*species+pendant_ID, family = "quasipoisson", data = final)
anova(m63, test = "Chisq")
e93 <- emmeans(m63, pairwise~species|temp)
e93
```



### Temperature Ranges per species from publications:
Salvia ranges from 10C to 25C (Cabrerra-Santos et al. 2022, Dashti et al. 2015)
Bromus ranges 
Layia ranges
Phacelia ranges


###GBIF citation
GBIF.org (31 January 2023) GBIF Occurrence Download  https://doi.org/10.15468/dl.vtkfem



###Ideas from Previous version
Purpose:
The purpose of this experiment is to determine if cooler temperatures, as seen under shrub canopies, could be used as an indicator for the germination success of both native and exotic plant species in arid ecosystems. 

Hypothesis:
We hypothesize that variations in fine scale temperature can act as a direct proxy for successful desert plant establishment and germination.

Predictions:
1) Fine scale temperature can be experimentally manipulated via heat lamps in an enclosed setting.
2) Plants will respond to varying fine scale temperatures.
3) The response to temperature will be species specific.
4) Responses to temperature will vary between native and exotic plant species.

Data:
All data can be access on KNB.
https://knb.ecoinformatics.org/view/doi:10.5063/F1GQ6W6R

Rough Ideas:
1)To connect this to shrub density I want to show that the cooler temperatures, as experienced under shrubs, can provide a benefit for species germination. The law table is meant to simulate these lower temperatures while the medium and high tables are meant to act as open areas at a moderate temperature and at extreme temperature.
2)There should be a visible difference between overall germination and mass between native and invasive species. If we can determine if invasives can germinate better under shrubs than in open areas then we can connect this to competition between natives and invasive.
3)Species should vary in their response to fine scale temperature since the range that they germinate vary from species to species. We should see that some natives germinate better at specific temperature while others do not.
4) We can connect this possibly to climate change. If we find that higher temperatures means a lower germination success then that can be the take-home message, that increasing temperatures have negative effects on desert plant species.



```{r}
### Test if table temp significant
Layia <- read.csv("All Temp Data.csv")
Brome <- read.csv("Brome Temp Sheet.csv")
Salvia <- read.csv("Salvia Temp Sheet.csv")
Phacelia <- read.csv("Phacelia Temp Sheet.csv")

### Merge all species temp data
Temp <- merge(Layia, Brome, all = TRUE)
Temp <- merge(Temp, Salvia, all = TRUE)
Temp <- merge(Temp, Phacelia, all = TRUE)


final_temp <- Temp %>%
  group_by(temp, species) %>%
  summarise(mean_table_temp = mean(temperature))

final2 <- merge(final, final_temp, all = TRUE) %>%
  na.omit()


```

```{r}
### Test to see if raw temp significant
library(glmmTMB)
temp <- glmmTMB(temperature ~ temp*species, data = Temp, family = "gaussian")
temp

```


### Proposed Boxplot figures and stats
```{r}
### Average Mass by mean temp
Mass_plot <- ggplot(final2, aes(mean_table_temp, average_mass, color = temp)) +
  geom_boxplot(width = 5, length = 10) +
  scale_fill_discrete(breaks=c("High", "Medium", "Low")) +
  facet_wrap(~species) + 
  scale_color_brewer(palette = "Set1") + theme_classic() + ylim(0,0.4)
Mass_plot


Germination_plot <- ggplot(final2, aes(mean_table_temp, germination, color = temp)) +
  geom_boxplot(width = 5) +
  scale_fill_discrete(breaks=c("High", "Medium", "Low")) +
  facet_wrap(~species) + 
  scale_color_brewer(palette = "Set1") + theme_classic() 
Germination_plot
 

Establishment_plot <- ggplot(final2, aes(mean_table_temp, establishment, color = temp)) +
  geom_boxplot(width = 5) +
  scale_fill_discrete(breaks=c("High", "Medium", "Low")) +
  facet_wrap(~species) + 
  scale_color_brewer(palette = "Set1") + theme_classic() 
Establishment_plot
```
```{r}
### Boxplot models
# Mass
model1 <- glm(mass ~ mean_table_temp*species+temp, family = "quasipoisson", data = final2)
broom::tidy(anova(model1, test = "Chisq"))
estimate1 <- emmeans(model1, pairwise~species|temp)
estimate1      # Broom::tidy() does not work on emmeans

# Establishment
model2 <- glm(establishment ~ mean_table_temp*species+temp, family = "quasipoisson", data = final2)
broom::tidy(anova(model2, test = "Chisq"))
estimate2 <- emmeans(model2, pairwise~species|mean_table_temp)
estimate2    # Broom::tidy() does not work on emmeans

# Germination
model3 <- glm(germination ~ mean_table_temp*species+temp, family = "quasipoisson", data = final2)
broom::tidy(anova(model3, test = "Chisq"))
estimate3 <- emmeans(model3, pairwise~species|temp)
estimate3    # Broom::tidy() does not work on emmeans
```



#### Proposed figures and stats
```{r}
### Treat Temp as Block

# Testing Mass, establishment, and germination with temp as a block/category by species (Need pendant ID)

m61 <- glm(mass ~ temp*species+pendant_ID, family = "quasipoisson", data = final)
broom::tidy(anova(m61, test = "Chisq"))
e91 <- emmeans(m61, pairwise~species|temp)
e91      # Broom::tidy() does not work on emmeans

m62 <- glm(establishment ~ temp*species+pendant_ID, family = "quasipoisson", data = final)
broom::tidy(anova(m62, test = "Chisq"))
e92 <- emmeans(m62, pairwise~species|temp)
e92

m63 <- glm(germination ~ temp*species+pendant_ID, family = "quasipoisson", data = final)
broom::tidy(anova(m63, test = "Chisq"))
e93 <- emmeans(m63, pairwise~species|temp)
e93



### Average Mass by mean temp
ggplot(final, aes(mean_temp, average_mass, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Mean Temperature", y = "Bimass per pot (g)")

model1 <- glm(average_mass ~ temp*species, family = "quasipoisson", data = final)
broom::tidy(anova(model1, test = "Chisq"))
em1 <- emmeans(model1, pairwise~temp|species)
em1

### Overall Establishment by mean temp
ggplot(final, aes(mean_temp, establishment, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Mean Temperature", y = "Establishment per pot")

model3 <- glm(establishment ~ temp*species, family = "quasipoisson", data = final)
broom::tidy(anova(model3, test = "Chisq"))
em3 <- emmeans(model3, pairwise~temp|species)
em3

### Overall Germination by mean temp
ggplot(final, aes(mean_temp, germination, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Mean Temperature", y = "Germination per pot")

model4 <- glm(germination ~ temp*species, family = "quasipoisson", data = final)
broom::tidy(anova(model4, test = "Chisq"))
em4 <- emmeans(model4, pairwise~temp|species)
em4


### Max Temp by Average mass by max temp
ggplot(final, aes(max_temp, average_mass, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Maximum Temperature", y = "Bimass per pot (g)")

model9 <- glm(average_mass ~ max_temp*species, family = "quasipoisson", data = final)
broom::tidy(anova(model9, test = "Chisq"))
em9 <- emmeans(model9, pairwise~species|max_temp)
em9

### Overall Establishment by max temp
ggplot(final, aes(max_temp, establishment, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Maximum Temperature", y = "Establishment per pot")

model11 <- glm(establishment ~ max_temp*species, family = "quasipoisson", data = final)
broom::tidy(anova(model11, test = "Chisq"))
em11 <- emmeans(model11, pairwise~species|max_temp)
em11

## #Overall Germination by max temp

ggplot(final, aes(max_temp, germination, color = temp),show.legend=FALSE) +
  geom_point() +
  facet_wrap(~species) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Maximum Temperature", y = "Germination per pot")

model12 <- glm(germination ~ temp*species, family = "quasipoisson", data = final)
broom::tidy(anova(model12, test = "Chisq"))
em12 <- emmeans(model12, pairwise~temp|species)
em12

```